RE: Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems

### 2023-05-16 rmd/reply2.Rmd
Update reply2.Rmd

@@

*A question that remains unclear to me is how omnivory is affecting the FCL in the simulations. It seems that all trophic species (B,C,P) are not supported in the simulation under all conditions. So basal species only or the loss of the consumer or predator. Consequently, extinction in the simulations can reduce FCL (correct me if wrong but the simulations start with three species, so species are not added or inserted). Is this the only way that food chain length can change? Or is food chain length a product of the dynamic interactions that can be influenced by the magnitude of the trophic contributions from different trophic levels. This would be consistent with a continuous measure of food chain length rather than another measure like the number of distinct trophic levels that occupy a patch? There is a lot of occupancy information added to the supplement but I had a hard time understanding from the text.*

*For the ecosystem size plot, when you have the straight chain the max FCL is 3 but when you add a some omnivory the max is 2, so a whole trophic level is lost. But when you go from weak omnivory to strong omnivory the max FCL stays the same. Looking at the figure 1 c (and from experience) the expectation is that as omnivory increases the FCL decreases. Now I am doubting that I understand the way the FCL is being determined. Also, in the supplement there are figures that show some FCL between 2 and 3 (Figure S3 and S4) but not sure what is happening.*

@@

@@

@@

@@

@@

@@

>>>>

> Thank you for your valuable feedback! Please see our point-by-point response below.

@@

> This is a great idea! We included a new hierarchical tree figure to show how different factors detemine the FCL response to ecosystem size/complexity (Figure 2 in the revised MS).
Also, we revised the figure captions to better guide readers.

*A question that remains unclear to me is how omnivory is affecting the FCL in the simulations. It seems that all trophic species (B,C,P) are not supported in the simulation under all conditions. So basal species only or the loss of the consumer or predator. Consequently, extinction in the simulations can reduce FCL (correct me if wrong but the simulations start with three species, so species are not added or inserted). Is this the only way that food chain length can change? Or is food chain length a product of the dynamic interactions that can be influenced by the magnitude of the trophic contributions from different trophic levels. This would be consistent with a continuous measure of food chain length rather than another measure like the number of distinct trophic levels that occupy a patch?*

> Our unclear explanation may have confused the reviewer. There are a number of cases where all species (B, C, P) coexist. "*...is food chain length a product of the dynamic interactions that can be influenced by the magnitude of the trophic contributions from different trophic levels.*" This is how we defined FCL in our model, which was articulated in equations 12 & 13.

*There is a lot of occupancy information added to the supplement but I had a hard time understanding from the text.*

> We appreciate your feedback. The figure captions were editted so the readers can better understand what those figures mean.
In particular, we have reworded the confusing term "occupancy" to "proportion of patch state" to clarify the y-axis.

*For the ecosystem size plot, when you have the straight chain the max FCL is 3 but when you add a some omnivory the max is 2, so a whole trophic level is lost.*

> Thank you, please let us clarify.
First, we defined FCL as trophic position, not as trophic level. Thus, the FCL can take continuous values.
With omnivory, the max is greater than 2 becuase of the coexistence of C and P.
P's trophic level depends on the relative abundance of B.
Thus, with omnivory, the FCL can be shorter than the chain motif even if the same set of species coexist.

*But when you go from weak omnivory to strong omnivory the max FCL stays the same. Looking at the figure 1 c (and from experience) the expectation is that as omnivory increases the FCL decreases. Now I am doubting that I understand the way the FCL is being determined. Also, in the supplement there are figures that show some FCL between 2 and 3 (Figure S3 and S4) but not sure what is happening.*

> Thank you for your input. "*Looking at the figure 1 c (and from experience) the expectation is that as omnivory increases the FCL decreases.*" -- The response of FCL to increasing omnivory can be more complex.
Weak omnivory can cause similar or even lower FCL than strong omnivory because the intraguild predator has a greater predation pressure on intraguild prey.
For the definition of FCL in our study, please see equations 12 & 13 -- it accounts for relative availability of B and C in a given habitat patch.

@@

> Thank you, we have revised figure captions.
Also, we clarified the values of ecosystem size or complexity in the main figures (both are randomly drawn from uniform distributions).

@@

> Thank you, we have revised figure captions.

@@

> Thank you! We have now added a color scale that indicate the relative reliance on B and C.
Meanwhile, we avoided to include FCL in the figure; this is because the relative reliance per se may not necessarily determine the FCL.
For example, weak omnivory could enhance the extirpation of intraguild prey, potentially resulting in a shorter FCL than that in strong omnivory.

@@

> Agreed -- there are two levels of productivity in our model, and this set up was unavoidable.
In the meantime, we feel that too much emphasis on this part may over-complicate the content, which is complex enough already (as you pointed out earlier in this round of review). In looking at the one-patch simulation, the FCL response to increased productivity can be well understood based on the single-patch analog. Thus, we decided not to delve into the specifics on this issue.

@@

> We are not sure if we correctly understood this comment, but we interpreted this comment suggesting to move the patch state figures to the maintext. We have now moved those figures to the maintext. In the meantime, we kept the text to explain those figures in the result section, since it seems inappropriate to mention those findings in the discussion section without mentioning them in the result.

@@

> We have defined the term in the Intro.
